Posterior summarisation in Bayesian phylogenetics using Tracer 1.7

### 2018-02-02 manuscript/tracer17.tex
edited new AR paragraph; please reformat to fit back on 3 pages, pretty please.

>>>>

Other packages are available for the post-processing of MCMC samples and are largely complementary to \tracer\. The R package `coda' \citep{plummer2006coda} provides some of the functionality of \tracer\ within the R programming environment. `AWTY' \citep{nylander2007awty} explores the convergence of the phylogenetic tree parameter itself across multiple MCMC runs.
%% AR - anything else? The MDS tree-space approaches of Hillis etc.?
